### 2023-02-27 text/ManuscriptDraft.Rmd
Point about small blob sizes and errors added

@@

>>>>

The binary masks included blobs with very low areas.

We must assume that small area sizes come with an increased risk of
error.

We calculated the area of each contour to see if the model accuracy was
dependent on object area.

@@

Importantly, we underline that the error associated with small object
areas are likely to be human error in the annotation process.
